# The learnerpkg Package

[![test-coverage](https://github.com/kristen-sauby/learnerpkg/actions/workflows/test_coverage.yml/badge.svg)](https://github.com/kristen-sauby/learnerpkg/actions/workflows/test_coverage.yml)
[![codecov](https://codecov.io/gh/kristen-sauby/learnerpkg/branch/main/graph/badge.svg?token=x4r6rOiG8y)](https://codecov.io/gh/kristen-sauby/learnerpkg)[![R](https://github.com/kristen-sauby/learnerpkg/actions/workflows/r.yml/badge.svg)](https://github.com/kristen-sauby/learnerpkg/actions/workflows/r.yml)

This is an example R package that includes examples of how to write functions, 
  how to test functions, how to include citations, how to use templates, and
  more.
Take a look at the package files on GitHub to see the behind-the-scenes code
that generated these pages and functionality.

## Installation

::: .pkgdown-devel
```{r, eval = FALSE}
# Install development version from GitHub
devtools::install_github("kristen-sauby/learnerpkg")
```
:::

## Usage

Get started with [learnerpkg](https://kristen-sauby.github.io/learnerpkg/):

```{r, eval = FALSE}
createSentence("I", "happily", "walked", "home")
```

## Building this package website

The `pkgdown` package was used to generate this website. 

To build a package site like this, follow the package instructions, including the following:

```{r, eval = FALSE}
# Start by running this to configure the package:
usethis::use_pkgdown()
# Build the site with this command
pkgdown::build_site()
```

On GitHub, you can set up GitHub Actions to build and publish your site every 
time you commit.
You can use GitHub pages to easily create the collection of HTML files that
encompasses the site. To build the GitHub pages, run the following:

```{r, eval = FALSE}
usethis::use_pkgdown_github_pages()
```
